Integer Programming Formulations for the Shared Multicast Tree Problem

### 2018-09-16 smt/sec6-exp.tex
some results for the additional experiments (meta heuristics) are now in Tab 4.

\textcolor{blue}{
To the best of our knowledge, SMT has not been studied extensively in terms of inexact methods.
However, there is a manifold of a thorough research of the minimum Steiner tree problem, with the possibility of adapting the methods on SMT.
We turn our attention to recently pusblished paper \citet{pajor18} which notains a metaheuristic algorithm for a fast generation of good solution to the Steiner tree problem.
The method is general, and is therefore very suitable for adaptation to our purposes.
The high level description is as follows:}
\begin{algorithm}
\textcolor{blue}{
Create an empty pool $P$ of elite solutions with capacity $\gamma=\left\lceil\sqrt{M/2}\right\rceil$\;
\For {$i\in \{1,\dots,M$\}} {
Generate a new solution $S$ using a constructive algorithm, local search, and randomization\;
\If {$i<\gamma$} {$P\leftarrow P\cup \{S\}$}
\Else {
$\hat{S}\leftarrow\arg\max_{S'\in P} c(S')$\;
\If {$c(\hat{S})> c(S)$}{$P\leftarrow P\cup \{S\}\setminus\{\hat{S}\}$}
$\hat{S}\leftarrow\arg\max_{S'\in P} c(S')$\;
Generate a solution $\tilde{S}$ by combining $S$ with solutions in $P$\;
\If {$c(\hat{S})> c(\tilde{S})$}{$P\leftarrow P\cup \{\tilde{S}\}\setminus\{\hat{S}\}$}
}
}
\Return $\arg\min_{S'\in P} c(S')$\;
 \caption{Outline of the metaheuristic algorithm}
}
\label{alg:meta}
\end{algorithm}
\textcolor{blue}{The construction procedure and local search is the adapted BIP algorithm together with refinements presented in \citet{ivanova16isco}.
The remaining parts of the algorithm are carried out as discussed in \citet{pajor18}.
The randomization is achieved by perturbing the edge costs in the input graph.
The obtained solution $S$ is evaluated with respect to the real (original) edge costs and added to the pool $P$ if the pool capacity is not filled.
If the pool is full and its worst solution $\hat{S}$ is worse than $S$, $\hat{S}$ is replaced by $S$ in $P$.
Then a new solution $\tilde{S}$ is constructed by combining some solution in $P$ with $S$. 
First, we adjust edge costs resulting in a modified input instance, 
and then run the construction and local search yielding $\tilde{S}$.
This new solution is again added to the pool if it is better than some solution already in $P$.
The adjustment of the edges tries to promote edges that appear in both $S$ and a selected solution in $P$. 
In that case, the original cost is preserved.
If an edge is present in only one of the two solutions, its cost is multiplied by a random integer between 100 and 500.
If an edge appears in neither of the solutions, its edge is multiplied by 1000, which makes it very unlikely to appear in the result $\tilde{S}$ of the combination.
}
\begin{table}[]
\centering
\textcolor{blue}{
\begin{tabular}{rrrrrrrrrrr}
\multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{3}{c}{5 min}  & \multicolumn{3}{c}{10 min} & \multicolumn{3}{c}{20 min}     \\\hline
\multicolumn{1}{l}{$|V|$} & \multicolumn{1}{l}{$|D|$} & \multicolumn{1}{l}{$\mathcal{X}_1$} & \multicolumn{1}{l}{$\mathcal{F}_1$} & \multicolumn{1}{l}{$\mathcal{M}$} & \multicolumn{1}{l}{$\mathcal{X}_1$} & \multicolumn{1}{l}{$\mathcal{F}_1$} & \multicolumn{1}{l}{$\mathcal{M}$} & \multicolumn{1}{l}{$\mathcal{X}_1$} & \multicolumn{1}{l}{$\mathcal{F}_1$} & \multicolumn{1}{l}{$\mathcal{M}$} \\\hline
20  & 10   &     &   &   &   &    &    &    &    &       \\
22  & 11   &     &   &   &   &    &    &    &    &       \\
24  & 12   &     &   &   &   &    &    &    &    &                                  
\end{tabular}
}
\caption{\textcolor{blue}{Comparison of the metaheuristic algorithm and solving IP models with imposed time-limit.}}
\label{tab:metamod}
\end{table}

>>>>

\textcolor{blue}{
To the best of our knowledge, SMT has not been studied extensively in terms of inexact methods.
However, there is a manifold of a thorough research of the minimum Steiner tree problem, with the possibility of adapting the methods on SMT.
We turn our attention to recently pusblished paper \citet{pajor18} which notains a metaheuristic algorithm for a fast generation of good solution to the Steiner tree problem.
The method is general, and is therefore very suitable for adaptation to our purposes.
The high level description is as follows:}
\begin{algorithm}
\textcolor{blue}{
Create an empty pool $P$ of elite solutions with capacity $\gamma=\left\lceil\sqrt{M/2}\right\rceil$\;
\For {$i\in \{1,\dots,M$\}} {
Generate a new solution $S$ using a constructive algorithm, local search, and randomization\;
\If {$i<\gamma$} {$P\leftarrow P\cup \{S\}$}
\Else {
$\hat{S}\leftarrow\arg\max_{S'\in P} c(S')$\;
\If {$c(\hat{S})> c(S)$}{$P\leftarrow P\cup \{S\}\setminus\{\hat{S}\}$}
$\hat{S}\leftarrow\arg\max_{S'\in P} c(S')$\;
Generate a solution $\tilde{S}$ by combining $S$ with solutions in $P$\;
\If {$c(\hat{S})> c(\tilde{S})$}{$P\leftarrow P\cup \{\tilde{S}\}\setminus\{\hat{S}\}$}
}
}
\Return $\arg\min_{S'\in P} c(S')$\;
 \caption{Outline of the metaheuristic algorithm}
}
\label{alg:meta}
\end{algorithm}
\textcolor{blue}{The construction procedure and local search is the adapted BIP algorithm together with refinements presented in \citet{ivanova16isco}.
The remaining parts of the algorithm are carried out as discussed in \citet{pajor18}.
The randomization is achieved by perturbing the edge costs in the input graph.
The obtained solution $S$ is evaluated with respect to the real (original) edge costs and added to the pool $P$ if the pool capacity is not filled.
If the pool is full and its worst solution $\hat{S}$ is worse than $S$, $\hat{S}$ is replaced by $S$ in $P$.
Then a new solution $\tilde{S}$ is constructed by combining some solution in $P$ with $S$. 
First, we adjust edge costs resulting in a modified input instance, 
and then run the construction and local search yielding $\tilde{S}$.
This new solution is again added to the pool if it is better than some solution already in $P$.
The adjustment of the edges tries to promote edges that appear in both $S$ and a selected solution in $P$. 
In that case, the original cost is preserved.
If an edge is present in only one of the two solutions, its cost is multiplied by a random integer between 100 and 500.
If an edge appears in neither of the solutions, its edge is multiplied by 1000, which makes it very unlikely to appear in the result $\tilde{S}$ of the combination.
}
\begin{table}[]
\centering
\setlength{\tabcolsep}{8pt} % Default value: 6pt
\renewcommand{\arraystretch}{1.4} % Default value: 1
\textcolor{blue}{
\begin{tabular}{rrrrrrrrrrr}
\multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{3}{c}{5 min}  & \multicolumn{3}{c}{10 min} & \multicolumn{3}{c}{20 min}     \\\hline
\multicolumn{1}{l}{$|V|$} & \multicolumn{1}{l}{$|D|$} & \multicolumn{1}{c}{$\mathcal{X}_1$} & \multicolumn{1}{c}{$\mathcal{F}_1$} & \multicolumn{1}{c}{$\mathcal{M}$} & \multicolumn{1}{c}{$\mathcal{X}_1$} & \multicolumn{1}{c}{$\mathcal{F}_1$} & \multicolumn{1}{c}{$\mathcal{M}$} & \multicolumn{1}{c}{$\mathcal{X}_1$} & \multicolumn{1}{c}{$\mathcal{F}_1$} & \multicolumn{1}{c}{$\mathcal{M}$} \\
\hline
18  & 12   &100.6&100.0&101.4&   &    &    &    &    &       \\
21  & 14   &     &   &   &   &    &    &    &    &       \\
24  & 16   &     &   &   &   &    &    &    &    &   \\     
\hline
20  & 10   &100.6&100.0&101.4&   &    &    &    &    &       \\
22  & 11   &     &   &   &   &    &    &    &    &       \\
24  & 12   &     &   &   &   &    &    &    &    &   \\                               
\hline
21  & 7    &100.6&100.0&101.4&   &    &    &    &    &       \\
24  & 8    &     &   &   &   &    &    &    &    &       \\
27  & 9    &     &   &   &   &    &    &    &    &                                  
\end{tabular}
}
\caption{\textcolor{blue}{Comparison of the metaheuristic algorithm and solving IP models with imposed time-limit.}}
\label{tab:metamod}
\end{table}
